Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
Lorraine's talk

\item \textbf{Lorraine Hwang, Joe Dumit, Alison Fish, Louise Kellogg, Mackenzie
Smith and Laura Soito: \textit{Software Attribution for Geoscience Applications in the
Computational Infrastructure for Geodynamics}}

>>>>

\item \textbf{Lorraine Hwang, Joe Dumit, Alison Fish, Louise Kellogg, Mackenzie
Smith and Laura Soito: \textit{Software Attribution for Geoscience Applications in the
Computational Infrastructure for Geodynamics}}
Lorraine Hwang presented experiences with CIG: the computational infrastructure
for Geodynamics, a community software with a worldwide user base. As others,
their main goals include high usability, sustainability, and reproducibility.
In order to achieve this, communication channels have been developed, like
mailing lists, wikis, workshops, hackathons, tutorials, and webinars. In order
to contribute to the infrastructure, codes have to adhere to specified minimum
standards, but ideals are also given to encourage reaching the aforementioned
goals. This includes, e.g., the use of version control, certain coding styles,
the presence and nature of code tests and documentation and certain user
workflows. In addition, various ways to cite efforts within the framework are
provided, including science papers, code papers, user manuals, and the website.
In an effort creating statistics of the resulting citations, $80\%$ of papers
that use CIG codes mention the code name, and about the same number includes a
citation. Only about $20\%$ acknowledge CIG. Within the same sample of papers,
about one fifth of use an URL to cite codes (including non-CIG codes), and only
about one eigth specifies the version used, showing that compared to other
codes, CIG seems to be much better cited. This, in part, is attributed to ideal
citation forms communicated to the community, and runtime tools that help
collecting a relevant citation list automatically.
